Transfer Learning in Visual and Relational Reasoning

### 2019-11-16 cvpr_submission/summary.tex
Minor typo corrections.

In this paper we quantified the impact of Transfer Learning on Visual Reasoning. 
We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performances on the CLEVR dataset for Image Resoning.

Taking that as a starting point and leveraging on the proposed taxonomy, we  have conducted an extensive set of experiments, with focus on impact of transfer learning in areas that might be considered as higher-level reasoning.
SAMNet demonstrated very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, we have managed to eleviate its performance even further.

Finally, we note that some of the proposed tasks (e.g. Train on all but \textit{t}) are complementary to the ones already well established in the literature, e.g. in taskonomy~\cite{zamir2018taskonomy}.
We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.

>>>>

In this paper, we quantified the impact of Transfer Learning on Visual Reasoning. 
We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performance on the CLEVR dataset for Image Reasoning.

Taking that as a starting point and leveraging the proposed taxonomy, we have conducted an extensive set of experiments, focusing on the impact of transfer learning in areas that might be considered as higher-level reasoning.
SAMNet demonstrates very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, can see its performance advanced even further.

Finally, we note that some of the proposed tasks (e.g. Train on all but \textit{t}) are complementary to ones already well established in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.
